---
title: "Stats 362 Final Project"
output: html_notebook
---

Will Hartog
12 March 2024

```{r}

library(ggplot2)

```
# Simulating the Interval

```{r}

draw_x = function(bern = 1, p = 0.5, a = 1, b = 1) {
  if (bern) {
    return((runif(1) < p))
  } else {
    return(rbeta(1, a, b))
  }
}

sim_interval = function(bern = 1, N = 1000, p = 0.5, a = 1, b = 1, g = 10, alpha = 0.05, theta = 0.5, c = 0.5) {
  K_min = replicate(g+1, 1)
  K_max = replicate(g+1, 1)
  K_tot = replicate(g+1, 1)
  mu_hat = 0.5
  sigma_hat2 = 0.25
  lambda = 0
  ms = (c(1:(g+1)) - 1)/g
  uppers = c()
  lowers = c()
  for (i in c(1:N)) {
    x = draw_x(bern, p, a, b)
    mu_hat = mu_hat * i/(i+1) + x/(i+1)
    sigma_hat2 = sigma_hat2 * i / (i+1) + (x - mu_hat) ** 2 / (i+1)
    
    K_min = K_min * (1 - pmin(lambda, c/ms) * (x - ms))
    K_max = K_max * (1 + pmin(lambda, c/(1-ms)) * (x - ms))
    K_tot = pmax(theta * K_max, (1 - theta) * K_min)
    
    int = which((K_tot < 1/alpha))
    uppers = c(uppers, (max(int) - 1)/g)
    lowers = c(lowers, (min(int) - 1)/g)
    
    lambda = sqrt(2 * log(2/alpha) / (sigma_hat2 * i * log(i+1)))
  }
  return(data.frame(uppers, lowers))
}

```

```{r}

sim = sim_interval(g = 1000, N = 1000, bern = 0, c = 0.75)
sim$trials = c(1:nrow(sim))

ggplot(data = sim, mapping = aes(x = trials)) + geom_line(aes(y = lowers)) + geom_line(aes(y = uppers))

```

# Simulating the Stopping Time

This function takes a granularity $g$ and target interval width and computes the amount of time to get there (and whether the true mean was covered).

```{r}

sim_to_width = function(bern = 1, p = 0.5, a = 1, b = 1, g = 10, alpha = 0.05, theta = 0.5, c = 0.5, target = 0.1) {
  K_min = replicate(g+1, 1)
  K_max = replicate(g+1, 1)
  K_tot = replicate(g+1, 1)
  mu = bern * p + (1-bern) * a/(a+b)
  mu_hat = 0.5
  sigma_hat2 = 0.25
  lambda = 0
  ms = (c(1:(g+1)) - 1)/g
  upper = 1
  lower = 0
  i = 0
  while ((upper - lower) > target) {
    i = i + 1
    x = draw_x(bern, p, a, b)
    mu_hat = mu_hat * i/(i+1) + x/(i+1)
    sigma_hat2 = sigma_hat2 * i / (i+1) + (x - mu_hat) ** 2 / (i+1)
    
    K_min = K_min * (1 - pmin(lambda, c/ms) * (x - ms))
    K_max = K_max * (1 + pmin(lambda, c/(1-ms)) * (x - ms))
    K_tot = pmax(theta * K_max, (1 - theta) * K_min)
    
    int = which((K_tot < 1/alpha))
    upper = (max(int) - 1)/g
    lower = (min(int) - 1)/g
    
    
    lambda = sqrt(2 * log(2/alpha) / (sigma_hat2 * i * log(i+1)))
  }
  contain = (mu <= upper) & (mu >= lower)
  return(c(i, contain))
}

```

This function just assumes we want to get the interval within target/2 on both sides of the mean, which is not always what we want but is simpler and faster to run.

```{r}

sim_to_fixed = function(bern = 1, p = 0.5, a = 1, b = 1, alpha = 0.05, theta = 0.5, c = 0.5, target = 0.1) {
  K_min = replicate(2, 1)
  K_max = replicate(2, 1)
  K_tot = replicate(2, 1)
  mu = bern * p + (1-bern) * a/(a+b)
  mu_hat = 0.5
  sigma_hat2 = 0.25
  lambda = 0
  ms = 0.5 + c(-1, 1) * target/2
  i = 0
  while (min(K_tot) <= 1/alpha) {
    i = i + 1
    x = draw_x(bern, p, a, b)
    mu_hat = mu_hat * i/(i+1) + x/(i+1)
    sigma_hat2 = sigma_hat2 * i / (i+1) + (x - mu_hat) ** 2 / (i+1)
    
    K_min = K_min * (1 - pmin(lambda, c/ms) * (x - ms))
    K_max = K_max * (1 + pmin(lambda, c/(1-ms)) * (x - ms))
    K_tot = pmax(theta * K_max, (1 - theta) * K_min)
    
    
    lambda = sqrt(2 * log(2/alpha) / (sigma_hat2 * i * log(i+1)))
    # in case we flame out
    if (min(K_tot) == 0) {
      return(Inf)
    }
  }
  return(i)
}

```

# Bernoulli Analysis

```{r}

counts_0.5 = replicate(1000, sim_to_fixed(target = 0.2))

hist(counts_0.5)
mean(counts_0.5)
sd(counts_0.5)


```

```{r}

counts_0.75 = replicate(1000, sim_to_fixed(c = 0.75, target = 0.2))

hist(counts_0.75)
mean(counts_0.75)
sd(counts_0.75)


```

```{r}

counts2 = c()
num_contain = 0
for (i in c(1:1000)) {
  sim = sim_to_width(c = 0.75)
  num_contain = num_contain + sim[2]
  counts2 = c(counts2, sim[1])
}

print(num_contain / 1000)

counts_0.75 = counts2
hist(counts_0.75)
mean(counts_0.75)

```

```{r}

num_iter = 1000

cs = seq(from = 0.1, to = 0.9, by = 0.01)

means = c()
sds = c()

for (c in cs) {
  counts_c = replicate(num_iter, sim_to_fixed(c = c, target = 0.2))
  means = c(means, mean(counts_c))
  sds = c(sds, sd(counts_c))
  print(c)
}

```

```{r}

c_df = data.frame(cs, means, sds)

ggplot(data = c_df, aes(x = cs, y = means)) + geom_line() + geom_ribbon(aes(ymin = means - 2.576 * sds/sqrt(num_iter), ymax = means + 2.576 * sds/sqrt(num_iter)), alpha = 0.3)


```

# Beta Analysis

```{r}

counts_0.5_unif = replicate(1000, sim_to_fixed(bern = 0, target = 0.2))

hist(counts_0.5_unif)
mean(counts_0.5_unif)
sd(counts_0.5_unif)

counts_0.75_unif = replicate(1000, sim_to_fixed(bern = 0, target = 0.2, c = 0.75))

hist(counts_0.75_unif)
mean(counts_0.75_unif)
sd(counts_0.75_unif)


```

```{r}

means_unif = c()
sds_unif = c()

for (c in cs) {
  counts_c = replicate(num_iter, sim_to_fixed(c = c, target = 0.2, bern = 0))
  means_unif = c(means_unif, mean(counts_c))
  sds_unif = c(sds_unif, sd(counts_c))
  print(c)
}

```

```{r}

c_df_unif = data.frame(cs, means_unif, sds_unif)

ggplot(data = c_df_unif, aes(x = cs, y = means_unif)) + geom_line() + geom_ribbon(aes(ymin = means_unif - 2.576 * sds_unif/sqrt(num_iter), ymax = means_unif + 2.576 * sds_unif/sqrt(num_iter)), alpha = 0.3)


```

```{r}

means_beta = c()
sds_beta = c()

for (c in cs) {
  counts_c = replicate(num_iter, sim_to_fixed(c = c, target = 0.2, bern = 0, a = 5, b = 5))
  means_beta = c(means_beta, mean(counts_c))
  sds_beta = c(sds_beta, sd(counts_c))
  print(c)
}

```


```{r}

c_df_beta = data.frame(cs, means_beta, sds_beta)

ggplot(data = c_df_beta, aes(x = cs, y = means_beta)) + geom_line() + geom_ribbon(aes(ymin = means_beta - 2.576 * sds_beta/sqrt(num_iter), ymax = means_beta + 2.576 * sds_beta/sqrt(num_iter)), alpha = 0.3)


```

```{r}

counts_1_beta = replicate(1000, sim_to_fixed(bern = 0, target = 0.2, c = 1, a = 5, b = 5))

hist(counts_1_beta)
mean(counts_1_beta)
sd(counts_1_beta)

```

```{r}

means_beta2 = c()
sds_beta2 = c()

for (c in cs) {
  counts_c = replicate(num_iter, sim_to_fixed(c = c, target = 0.2, bern = 0, a = 2, b = 2))
  means_beta2 = c(means_beta2, mean(counts_c))
  sds_beta2 = c(sds_beta2, sd(counts_c))
  print(c)
}

```


```{r}

c_df_beta2 = data.frame(cs, means_beta2, sds_beta2)

ggplot(data = c_df_beta2, aes(x = cs, y = means_beta2)) + geom_line() + geom_ribbon(aes(ymin = means_beta2 - 2.576 * sds_beta2/sqrt(num_iter), ymax = means_beta2 + 2.576 * sds_beta2/sqrt(num_iter)), alpha = 0.3)


```

```{r}

df_total = data.frame(cs, means, sds, means_unif, sds_unif, means_beta, sds_beta, means_beta2, sds_beta2)

View(df_total)
colnames(df_total)[6] = 'means_beta5'
colnames(df_total)[7] = 'sds_beta5'

write.csv(df_total, 'stats_362_sims.csv')

```
